Writing a reproducible paper with RStudio and Quarto

### 2023-04-03 paper.qmd
Update links to gdrive.

-   ...download the 3 input files we created --- `paper.qmd`, `references.bib` and `data.csv` --- from [this folder](https://drive.google.com/drive/u/0/folders/1eT_9WaineZRB-nw-cQhNOy16sWhd_t2s). Ignore the other files.
-   ...finally store all files from above together in one folder (and use this folder as your working directory later on).

@@

[Download these files](https://drive.google.com/drive/u/0/folders/1eT_9WaineZRB-nw-cQhNOy16sWhd_t2s) and save them into a folder. Close R/Rstudio and directly open `paper.qmd` with RStudio. Doing so assures that the working directory is set to the folder that contains `paper.qmd` and the other files.[^1]

@@

Below we import an exemplary dataset (you can find `data.csv` in the [folder](https://drive.google.com/drive/u/0/folders/1eT_9WaineZRB-nw-cQhNOy16sWhd_t2s) with the other files).

>>>>

-   ...download the 3 input files we created --- `paper.qmd`, `references.bib` and `data.csv` --- from [this folder](https://drive.google.com/drive/folders/1jDPpXdX6dusXpKkXEhDGujWDGf52TaxD?usp=sharing). Ignore the other files.
-   ...finally store all files from above together in one folder (and use this folder as your working directory later on).

@@

[Download these files](https://drive.google.com/drive/folders/1jDPpXdX6dusXpKkXEhDGujWDGf52TaxD?usp=sharing) and save them into a folder. Close R/Rstudio and directly open `paper.qmd` with RStudio. Doing so assures that the working directory is set to the folder that contains `paper.qmd` and the other files.[^1]

@@

Below we import an exemplary dataset (you can find `data.csv` in the [folder](https://drive.google.com/drive/folders/1jDPpXdX6dusXpKkXEhDGujWDGf52TaxD?usp=sharing) with the other files).
